Title Goes Here

### 2024-05-13 analysis/paper/paper.qmd
exploring EEO

```{r}
# EEO
library(stringr)
library(dplyr)
library(stopwords)
library(tidyverse)
library(tm)

@@

EEO <- jobdata %>%
  select(equal_employment_opportunity_statement)

@@

@@

EEO_word <- EEO_clean %>%
   unnest_tokens(word, text) %>%
  anti_join(get_stopwords()) %>%
  count(word, sort = TRUE)
```

>>>>

```{r}
# EEO
library(stringr)
library(dplyr)
library(stopwords)
library(tidyverse)
library(tidytext)
library(tm)

@@

EEO <- jobdata %>%
  select(equal_employment_opportunity_statement) %>% 
  drop_na

@@

ggplot(EEO_wordcount) +
  aes(word_count) +
  geom_histogram()

@@

# this doesn't work, need help to troubleshoot
EEO_word <- EEO_clean %>%
   unnest_tokens(word, 
                 equal_employment_opportunity_statement) %>%
  anti_join(get_stopwords()) %>%
  count(word, sort = TRUE)
```
